---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![stability-unstable](https://img.shields.io/badge/stability-unstable-yellow.svg)](https://github.com/joethorley/stability-badges#unstable)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/poispkgs.svg?branch=master)](https://travis-ci.org/poissonconsulting/poispkgs)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/poispkgs?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/poispkgs)
[![codecov](https://codecov.io/gh/poissonconsulting/poispkgs/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poispkgs)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://opensource.org/licenses/GPL-3.0)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/poispkgs)](https://cran.r-project.org/package=poispkgs)

# poispkgs

Attaches CRAN and GitHub Packages used in Poison Consulting analyses.

## Demonstration
```{r}
search()
library(poispkgs)
search()
```

## Installation

```
# install.packages("devtools")
devtools::install_github("poissonconsulting/poispkgs")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poispkgs/issues).

[Pull requests](https://github.com/poissonconsulting/poispkgs/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## Creditation

The code to attach lots of packages is based on that in the [tidyverse](https://github.com/tidyverse/tidyverse) R package.
