---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/poispkgs.svg?branch=master)](https://travis-ci.org/poissonconsulting/poispkgs)
[![codecov](https://codecov.io/gh/poissonconsulting/poispkgs/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poispkgs)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# poispkgs

An R package to attach CRAN and GitHub Packages used in Poison Consulting analyses.

## Demonstration
```{r}
search()
library(poispkgs)
search()
```

## Installation

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("poispkgs")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poispkgs/issues).

[Pull requests](https://github.com/poissonconsulting/poispkgs/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/poispkgs/blob/master/CONDUCT.md). 
By participating in this project you agree to abide by its terms.
