---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/license/mit/)
<!-- badges: end -->

# poispkgs

An R package to attach CRAN and GitHub Packages commonly used in Poisson Consulting analyses in the preferred order

## Demonstration
```{r}
library(poispkgs)
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/poispkgs)
```{r, eval = FALSE}
# install.packages("pak", repos = sprintf("https://r-lib.github.io/p/pak/stable/%s/%s/%s", .Platform$pkgType, R.Version()$os, R.Version()$arch))
pak::pak("poissonconsulting/poispkgs")
```

## Quiet

To suppress the start up messages use
```{r}
options(poispkgs.quiet = TRUE)
```

## Usage

To add a package to poispkgs, add the package to the Imports section of the DESCRIPTION. For Poisson packages, add the GitHub address of the package to the remotes section of the DESCRIPTION. This will ensure that we're using the developmental version. Also, add packages to one or more categories in `pkg-list.R`.

## Code of Conduct

Please note that the poispkgs project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
