---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/poissonconsulting/poispkgs/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/poispkgs/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/poispkgs/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poispkgs?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

# poispkgs

An R package to attach CRAN and GitHub Packages commonly used in Poisson Consulting analyses in the preferred order

## Demonstration
```{r}
library(poispkgs)
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/poispkgs)
```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/poispkgs")
```

## Quiet

To suppress the start up messages use
```{r}
options(poispkgs.quiet = TRUE)
```

## Code of Conduct

Please note that the poispkgs project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
