---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/license/mit/)
<!-- badges: end -->

# poispkgs

An R package to attach CRAN and GitHub Packages commonly used in Poisson Consulting analyses in the preferred order

## Demonstration
```{r}
library(poispkgs)
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/poispkgs)
```{r, eval = FALSE}
# install.packages("pak", repos = sprintf("https://r-lib.github.io/p/pak/stable/%s/%s/%s", .Platform$pkgType, R.Version()$os, R.Version()$arch))
pak::pak("poissonconsulting/poispkgs")
```

## Quiet

To suppress the start up messages use
```{r}
options(poispkgs.quiet = TRUE)
```

## Usage

To add package to poispkgs, add it to imports in DESCRIPTION, make sure you have the GitHub address in remotes for Poisson packages to ensure we have the developmental version.
And add it to one or more categories in pkg-list.R.

## Code of Conduct

Please note that the poispkgs project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
